\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-09 analysis/manuscript.Rmd
group programmatically

subject_table %>%
  group_by(subject_area) %>%
  arrange(top_level, .by_group = TRUE) %>% 
  ungroup() %>%
  select(-subject_area) %>%
            kbl(booktabs = TRUE, "latex", format.args = list(big.mark = ","), digits = 1, escape = FALSE,
                  caption = "Invoice channels by discipline 2015-2019.",
                  position = "H",
      col.names = c("Subject", "OA articles", "Author", "Agreement", "Fee waived", "Other"),
       linesep = "",
      align = "lrrrrr") %>%
  add_header_above(c(" " = 2, "Invoice channel (in %)" = 4)) %>%
  # manual, puh, not good 
  pack_rows("Health Sciences", 1, 5) %>%
  pack_rows("Life Sciences", 6, 10) %>%
  pack_rows("Health Sciences", 11, 20) %>%
  pack_rows("Health Sciences", 21, 26) %>%
  kable_styling(latex_options = c("scale_down"))
```

>>>>

subject_table_ <- subject_table %>%
  group_by(subject_area) %>%
  arrange(top_level, .by_group = TRUE) %>% 
  ungroup() 
subject_table_ %>%
  select(-subject_area) %>%
            kbl(booktabs = TRUE, "latex", format.args = list(big.mark = ","), digits = 1, escape = FALSE,
                  caption = "Invoice channels by discipline 2015-2019.",
                  position = "H",
      col.names = c("Subject", "OA articles", "Author", "Agreement", "Fee waived", "Other"),
       linesep = "",
      align = "lrrrrr") %>%
  add_header_above(c(" " = 2, "Invoice channel (in %)" = 4)) %>%
  pack_rows(index = table(subject_table_$subject_area)) %>%
  kable_styling(latex_options = c("scale_down"))
```
